Statistical Machine Learning Models on A Bank Marketing dataset

### 2025-12-08 Slides.Rmd
Update slides with cleaned code and final results

---
title: "Statistical Machine Learning Models on A Bank Marketing dataset"
author: "Sandra, Tigist, Mussa Hassen, Waddah"
subtitle: 'Colorado State University, DSCI 445: Statistical Machine Learning, Dr.Andee
  Kaplan'
output:
  ioslides_presentation: 
    css: styles.css

@@

## Project Motivation & Business Problem
* **Discuss:** The bank's need for efficient marketing and the high cost of telemarketing campaigns. The goal is to maximize the success rate by predicting customer subscription.
* **Discuss:** The challenge of less positive class (imbalanced data) and why prediction accuracy is crucial.
* **Image/Plot Idea:** A simple, high-level info graphic of a marketing campaign funnel, highlighting the bottleneck/drop-off point.

[Image of a marketing funnel illustrating customer conversion]

@@

@@

@@

@@

## KNN 1/3: Feature Preparation 
* **Discuss:** **KNN** requires scaling: all numeric predictors were **standardized** (mean=0, SD=1) to prevent features with larger scales from dominating the distance calculation.
* **Discuss:** The non-parametric nature means **no explicit feature selection** via coefficients, but the scaling step is vital for ensuring equal contribution from all dimensions.
* **Image/Plot Idea:** A visual comparison: a scatter plot of two features *unscaled* vs. the same features *scaled/standardized*. 
```{r, echo=FALSE, results='asis'}

library(dplyr)
library(class)
library(caret)

set.seed(123)
train_index <- sample(nrow(bank_full), 0.8 * nrow(bank_full))
bank_train <- bank_full[train_index, ]
bank_test  <- bank_full[-train_index, ]

numeric_vars <- names(bank_full)[sapply(bank_full, is.numeric)]
numeric_vars <- setdiff(numeric_vars, "y")

train_x <- bank_train[, numeric_vars, drop = FALSE]
test_x  <- bank_test[, numeric_vars, drop = FALSE]

train_x <- bank_train[, numeric_vars]
test_x  <- bank_test[, numeric_vars]

@@

train_y <- bank_train$y
test_y  <- bank_test$y

best_k <- 5

par(mfrow = c(1, 2))

plot(
  bank_full$age, bank_full$balance,
  xlab = "Age", ylab = "Balance",
  main = "Unscaled Features"
)

scaled_two <- scale(bank_full[, c("age", "balance")])

plot(
  scaled_two[, "age"], scaled_two[, "balance"],
  xlab = "Scaled Age", ylab = "Scaled Balance",
  main = "Scaled Features (mean = 0, sd = 1)"
)

par(mfrow = c(1, 1))

i <- 1  
test_point <- test_x_scaled[i, , drop = FALSE]

distances <- apply(
  train_x_scaled,
  1,
  function(row) sqrt(sum((row - test_point)^2))
)

nn_idx <- order(distances)[1:best_k]

knn_demo_pred <- knn(
  train = train_x_scaled,
  test  = test_point,
  cl    = train_y,
  k     = best_k
)

cat("Test customer index:", i, "\n")
cat("KNN predicted class:", knn_demo_pred, "\n")
cat("True class:", test_y[i], "\n\n")

cat("Neighbor outcome breakdown:\n")
print(table(train_y[nn_idx]))

cat("\nNearest neighbor details:\n")
print(head(bank_train[nn_idx, c("age", "balance", "duration", "campaign", "y")]))

```
```{r, echo=FALSE, results='asis'}
library(class)

numeric_vars <- names(bank_full)[sapply(bank_full, is.numeric)]
numeric_vars <- setdiff(numeric_vars, "y")

train_x <- bank_train[, numeric_vars, drop = FALSE]
test_x  <- bank_test[, numeric_vars, drop = FALSE]

train_y <- bank_train$y
test_y  <- bank_test$y

knn_pred <- knn(
  train = train_x_scaled,
  test  = test_x_scaled,
  cl    = train_y,
  k     = 5
)

knn_accuracy <- mean(knn_pred == test_y)
knn_error <- 1 - knn_accuracy
cat("KNN Test Accuracy:", round(knn_accuracy * 100, 2), "%\n")
cat("KNN Test Error:", round(knn_error * 100, 2), "%\n")

```
```

## KNN 2/3: Hyperparameter Tuning 
* **Discuss:** The sole hyperparameter, **$k$** (the number of neighbors), determines the model's complexity (i.e., the bias-variance trade-off).
* **Discuss:** **5-Fold Cross-Validation** was performed across a range of $k$ values to find the optimal $k$ that minimized the mean CV error.
* **Image/Plot Idea:** A plot showing **CV Test Error vs. $k$**, illustrating the U-shape curve where the optimal $k$ is selected.
```{r, echo=FALSE, results='asis'}
library(class)
library(caret)

set.seed(123)

k_values <- 1:25                  
cv_error <- numeric(length(k_values))

@@

best_k <- k_values[which.min(cv_error)]
best_k
plot(
  k_values, cv_error,
  type = "b",
  xlab = "Number of neighbors (k)",
  ylab = "5-fold CV Test Error",
  main = "KNN: 5-fold CV Test Error vs k"
)

abline(v = best_k, lty = 2)

## KNN 3/3: Evaluation & Test Performance
* **Discuss:** The final KNN model (with optimal $k$) was applied to the **Test Set**. Evaluate performance using **AUC** and compare it to the LogReg models.
* **Discuss:** KNN generally provides a good intermediate balance—often capturing non-linearity better than LogReg but being less computationally expensive than boosting.
* **Image/Plot Idea:** A brief table comparing the **AUC** and **Recall** of the best LogReg model and the final KNN model.

```{r, echo=FALSE, results='asis'}
library(pROC)
library(caret)

set.seed(123)

@@

logit_model <- glm(y ~ ., data = bank_train, family = binomial)

logit_prob <- predict(logit_model, newdata = bank_test, type = "response")
logit_pred <- ifelse(logit_prob >= 0.5, "yes", "no")
logit_pred <- factor(logit_pred, levels = c("no", "yes"))

logit_roc <- roc(response = test_y_fac, predictor = logit_prob, levels = c("no", "yes"))
logit_auc <- as.numeric(auc(logit_roc))

logit_cm     <- confusionMatrix(logit_pred, test_y_fac, positive = "yes")
logit_recall <- logit_cm$byClass["Recall"]

results <- data.frame(
  Model  = c("Logistic Regression", paste0("KNN (k = ", best_k, ")")),
  AUC    = c(logit_auc, knn_auc),
  Recall = c(as.numeric(logit_recall), as.numeric(knn_recall))
)

results$AUC    <- round(results$AUC, 3)
results$Recall <- round(results$Recall, 3)

results

---
# 3. Boosting Model (High Predictive Benchmark)
---

## Boosting 1/3: Model Formulation
* **Discuss:** **Boosting** (e.g., Gradient Boosting) is an ensemble method that sequentially builds weak learners (trees) to minimize the classification error of the previous step.
* **Discuss:** This model is expected to be our **highest-performing benchmark** but sacrifices interpretability due to its complex, additive structure.
* **Image/Plot Idea:** A conceptual diagram illustrating the boosting process (weak learners combining sequentially to form a strong learner). 
```{r, echo=FALSE, results='asis'}
library(gbm)

bank_train$y_num <- ifelse(bank_train$y == "yes", 1, 0)
bank_test$y_num  <- ifelse(bank_test$y  == "yes", 1, 0)

set.seed(123)

boost_model <- gbm(
  formula = y_num ~ . - y,       
  data = bank_train,
  distribution = "bernoulli",   
  n.trees = 1000,                
  interaction.depth = 3,         
  shrinkage = 0.01,             
  n.minobsinnode = 10,
  verbose = FALSE
)

boost_prob <- predict(
  boost_model,
  newdata = bank_test,
  n.trees = 1000,
  type = "response"
)

boost_pred <- ifelse(boost_prob > 0.5, "yes", "no")

boost_accuracy <- mean(boost_pred == bank_test$y)
boost_error    <- 1 - boost_accuracy

cat("Boosting Test Accuracy:", round(boost_accuracy * 100, 2), "%\n")
cat("Boosting Test Error:",   round(boost_error * 100, 2), "%\n")

plot(
  boost_model$train.error,
  type = "l",
  xlab = "Number of Trees (Iterations)",
  ylab = "Training Loss",
  main = "Boosting: Sequential Error Reduction"
)

## Boosting 2/3: Hyperparameter Tuning 
* **Discuss:** Multiple hyperparameters were tuned using **Cross-Validation**, including the **number of trees** (M), **interaction depth** (complexity of weak learners), and **learning rate** ($\eta$).
* **Discuss:** The tuning process involves finding the right balance between these parameters to ensure the model generalizes well without overfitting the training data.
* **Image/Plot Idea:** A plot showing the **Error Rate vs. Number of Trees**, highlighting where the Test Error flattens or begins to increase (overfitting).
```{r, echo=FALSE, results='asis'}
boost_model <- gbm(
  formula = y_num ~ . - y,
  data = bank_train,
  distribution = "bernoulli",
  n.trees = 1000,
  interaction.depth = 3,
  shrinkage = 0.01,
  n.minobsinnode = 10,
  verbose = FALSE
)

M_values <- seq(50, 1000, by = 50)
test_error <- numeric(length(M_values))

@@

  prob_M <- predict(
    boost_model,
    newdata = bank_test,
    n.trees = M,
    type = "response"
  )

  pred_M <- ifelse(prob_M > 0.5, "yes", "no")
  test_error[i] <- mean(pred_M != bank_test$y)
}

@@

cat("Best number of trees based on Test Error:", best_M, "\n")

plot(
  M_values, test_error,
  type = "b",
  xlab = "Number of Trees (M)",
  ylab = "Test Error",
  main = "Boosting: Test Error vs Number of Trees"
)

abline(v = best_M, lty = 2)

## Boosting 3/3: Evaluation & Importance 
* **Discuss:** The final Boosting model was evaluated on the **Test Set**. Confirm that it achieved the **highest AUC**, setting the benchmark for predictive accuracy.
* **Discuss:** While coefficients are not available, discuss the model's **Variable Importance Plot** as the only glimpse into its internal workings.
* **Image/Plot Idea:** The **Variable Importance Plot** from the Boosting model, which should confirm that the most important features align reasonably well with LogReg's significant coefficients.
```{r, echo=FALSE, results='asis'}
library(pROC)

boost_prob <- predict(
  boost_model,
  newdata = bank_test,
  n.trees = 1000,       
  type = "response"
)

test_y_fac <- factor(bank_test$y, levels = c("no", "yes"))

boost_roc <- roc(
  response  = test_y_fac,
  predictor = boost_prob,
  levels    = c("no", "yes")
)

boost_auc <- as.numeric(auc(boost_roc))
cat("Boosting Test AUC:", round(boost_auc, 3), "\n")

vi <- summary(boost_model, plotit = FALSE)

top_n <- min(10, nrow(vi))
vi_top <- vi[1:top_n, ]

barplot(
  height = vi_top$rel.inf,
  names.arg = vi_top$var,
  las = 2,
  ylab = "Relative Influence",
  main = "Boosting: Variable Importance (Top Features)"
)

## Results: Comparative Evaluation (Slide 13). #MUSSA
* **Discuss:** Present the **Final Summary Table** comparing the Test Set performance (AUC, Recall, Accuracy) of all models (**Best LogReg**, **KNN**, **Boosting**).
* **Discuss:** Visually compare the models using the **Combined ROC Curve Plot** and discuss which model dominates the space.
* **Image/Plot Idea:** The **Combined ROC Curve Plot** comparing all three final models (LogReg, KNN, and Boosting).

## The Trade-Off / Business Impact  #MUSSA
* **Discuss:** Reiterate the central trade-off: **Boosting** is the best *predictor*, but the **Regularized Logistic Regression** offers the most *interpretable* and *actionable* insights for the bank.
* **Discuss:** Final actionable advice for the bank: use **LogReg insights** to design campaigns and **Boosting** for a final scoring model if maximum predictive accuracy is needed.
* **Image/Plot Idea:** A visual metaphor (e.g., a scale or seesaw) contrasting "High Performance" vs. "High Interpretability."
* **Discuss:** How the **chosen model** (Balancing performance and interpretability) can lead to **cost savings** and **higher ROI** for future campaigns.
* **Discuss:** Briefly touch upon **regulatory/ethical implications** in banking and the need to justify predictions (further supporting the value of interpretability).
* **Image/Plot Idea:** A currency symbol or a bar chart showing the conceptual increase in ROI due to better targeting.

## Discussion: Limitations & Future Work (Slide 14)  #MUSSA
* **Discuss:** Acknowledge limitations, such as not using **time-series analysis** or fully accounting for the dependency of the 'duration' feature.
* **Discuss:** Suggest future improvements: Exploring advanced techniques like **resampling methods** (SMOTE) to handle imbalance better or trying **Deep Learning** models.

## References (Slide 15)
* **Discuss:** Simply list the required references for the data source and any major methodology papers.
* **Discuss:** Provide contact information for questions.
* Thank you
* **Image/Plot Idea:** The official UCI ML Repository logo and your contact email.

>>>>

---
title: "Statistical Machine Learning Models on A Bank Marketing dataset"
author: "Sandra, Tigist, Mussa Hassen, Waddah"
subtitle: 'Colorado State University, DSCI 445: Statistical Machine Learning, Dr.Andee
  Kaplan'
output:
  ioslides_presentation:
    widescreen: true
---

@@

## Project Motivation & Business Problem (S)
- Telemarketing campaigns are expensive, time-consuming, and have very low success rates. The bank wants to improve efficiency by identifying which clients are most likely to subscribe.
- The dataset has a severe class imbalance: only a small fraction of customers subscribe to the term deposit. This makes prediction difficult and increases the risk of false negatives.
- Improving predictive accuracy would allow the bank to target fewer customers, reduce costs, and increase return on investment (ROI) for future campaigns.

--- 
```{r, echo=FALSE}
library(ggplot2)

ggplot(bank_full, aes(x = y, fill = y)) +
geom_bar() +
scale_fill_manual(values = c("#2E86C1", "#F39C12")) +
labs(
title = "Term Deposit Subscription (Severe Class Imbalance)",
x = "Subscribed?",
y = "Count"
) +
theme_minimal(base_size = 14)

@@

* Cell phone calls perform best

@@

* Past success predicts new success

@@

* More calls = worse results

@@

## KNN 1/3: Feature Preparation 
* **KNN** requires scaling: all numeric predictors were **standardized** (mean=0, SD=1) to prevent features with larger scales from dominating the distance calculation.
* The non-parametric nature means **no explicit feature selection** via coefficients, but the scaling step is vital for ensuring equal contribution from all dimensions.

```{r knn-prep, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(class)
library(caret)

# Use the same train/test split from appendix
numeric_vars <- names(train_data)[sapply(train_data, is.numeric)]
numeric_vars <- setdiff(numeric_vars, c("y_num", "residuals"))

train_x <- train_data[, numeric_vars]
test_x  <- test_data[, numeric_vars]

@@

train_y <- train_data$y
test_y  <- test_data$y

# Visualization
par(mfrow = c(1, 2))
plot(
  train_data$age, train_data$balance,
  xlab = "Age", ylab = "Balance",
  main = "Unscaled Features"
)

scaled_two <- scale(train_data[, c("age", "balance")])
plot(
  scaled_two[, "age"], scaled_two[, "balance"],
  xlab = "Scaled Age", ylab = "Scaled Balance",
  main = "Scaled Features"
)
par(mfrow = c(1, 1))

# Calculate accuracy with k=5 for demonstration
knn_pred_demo <- knn(train = train_x_scaled, test = test_x_scaled, cl = train_y, k = 5)
knn_accuracy_demo <- mean(knn_pred_demo == test_y)
```

**Test Accuracy (k=5):** `r round(knn_accuracy_demo * 100, 2)`%
---

## KNN 2/3: Hyperparameter Tuning 
* The sole hyperparameter, **$k$** (the number of neighbors), determines the model's complexity (i.e., the bias-variance trade-off).
* **5-Fold Cross-Validation** was performed across a range of $k$ values to find the optimal $k$ that minimized the mean CV error.

```{r knn-tuning, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
set.seed(445)

k_values <- seq(1, 25, by = 2)
cv_error <- numeric(length(k_values))

@@

best_k <- k_values[which.min(cv_error)]

plot(
  k_values, cv_error,
  type = "b",
  xlab = "Number of neighbors (k)",
  ylab = "5-fold CV Test Error",
  main = "KNN: CV Test Error vs k"
)
abline(v = best_k, lty = 2, col = "red")
text(best_k, max(cv_error), paste("Best k =", best_k), pos = 4, col = "red")
```

**Optimal k:** `r best_k`
--- 
## KNN 3/3: Evaluation & Test Performance
* The final KNN model (with optimal $k$) was applied to the **Test Set**. We evaluate performance using **AUC** and compare it to the LogReg models.
* KNN generally provides a good intermediate balance—often capturing non-linearity better than LogReg but being less computationally expensive than boosting.

```{r knn-results, echo=FALSE, message=FALSE, warning=FALSE}
library(pROC)

@@

cm_knn <- knn_cm
roc_knn <- knn_roc
auc_knn <- knn_auc

# Results table
results <- data.frame(
  Model  = c("KNN", "Baseline Logit", "Ridge", "LASSO"),
  AUC    = c(knn_auc, auc(roc_baseline), auc(roc_ridge), auc(roc_lasso)),
  Sensitivity = c(as.numeric(knn_recall), 
                  cm_baseline$byClass["Sensitivity"],
                  cm_ridge$byClass["Sensitivity"],
                  cm_lasso$byClass["Sensitivity"])
)

results$AUC <- round(results$AUC, 3)
results$Sensitivity <- round(results$Sensitivity, 3)

knitr::kable(results)
```

---
# 3. Boosting Model (High Predictive Benchmark)
---
```{r boosting-setup, echo=FALSE, message=FALSE, warning=FALSE}
library(gbm)
library(pROC)
library(caret)

# Clean up train_data if needed
if ("residuals" %in% colnames(train_data)) {
  train_data$residuals <- NULL
}

# Create numeric response for boosting
train_data$y_num <- ifelse(train_data$y == "yes", 1, 0)
test_data$y_num  <- ifelse(test_data$y == "yes", 1, 0)

# Fit boosting model
boost_model <- gbm(
  y_num ~ . - y,         
  data = train_data,
  distribution = "bernoulli",
  n.trees = 1500,       
  shrinkage = 0.01,
  interaction.depth = 3,
  bag.fraction = 0.5,
  verbose = FALSE
)

best_trees <- gbm.perf(boost_model, method = "OOB", plot.it = FALSE)

# Predictions
boost_prob <- predict(boost_model, test_data, n.trees = best_trees, type = "response")
boost_pred <- factor(ifelse(boost_prob > 0.5, "yes", "no"), levels = c("no", "yes"))

# Confusion matrix
cm_boost <- confusionMatrix(boost_pred, test_data$y, positive = "yes")

# ROC and AUC
roc_boost <- roc(test_data$y, boost_prob)
auc_boost <- auc(roc_boost)
```

## Boosting 1/3: Model Formulation

- Boosting builds many small trees sequentially, each fixing errors from the previous one.
- These weak learners combine into a strong model that captures complex, non-linear patterns.
- It usually achieves the highest accuracy/AUC, but is less interpretable than LogReg or KNN.
```{r boosting-viz, echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.width=6}
plot(
  boost_model$train.error,
  type = "l",
  xlab = "Number of Trees (Iterations)",
  ylab = "Training Loss",
  main = "Boosting: Sequential Error Reduction",
  col = "steelblue",
  lwd = 2
)
```

## Boosting 2/3: Hyperparameter Tuning 
- We tuned the number of trees using OOB error estimation to prevent overfitting.
- The OOB method selected **`r best_trees`** trees as optimal.
- This choice balances model complexity and generalization.
```{r boosting-tuning, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
# Test different numbers of trees
M_values <- seq(50, 1500, by = 50)
test_error <- numeric(length(M_values))

@@

  prob_M <- predict(
    boost_model,
    newdata = test_data,
    n.trees = M,
    type = "response"
  )

  pred_M <- ifelse(prob_M > 0.5, "yes", "no")
  test_error[i] <- mean(pred_M != test_data$y)
}

@@

plot(
  M_values, test_error,
  type = "b",
  xlab = "Number of Trees (M)",
  ylab = "Test Error",
  main = "Boosting: Test Error vs Number of Trees",
  col = "steelblue",
  lwd = 2
)
abline(v = best_M, lty = 2, col = "red", lwd = 2)
text(best_M, max(test_error), paste("Best M =", best_M), pos = 4, col = "red")
```

**Optimal number of trees (via test error):** `r best_M`

## Boosting 3/3: Evaluation & Importance 
- The final Boosting model achieved the highest AUC and sensitivity among all models tested.
- Variable Importance Plot shows which features influence predictions most.
- The importance rankings align with key predictors identified by Logistic Regression.
```{r boosting-results, echo=FALSE, message=FALSE, warning=FALSE}
# Variable importance
vi <- summary(boost_model, plotit = FALSE)
top_n <- min(10, nrow(vi))
vi_top <- vi[1:top_n, ]

barplot(
  height = vi_top$rel.inf,
  names.arg = vi_top$var,
  las = 2,
  ylab = "Relative Influence",
  main = "Boosting: Variable Importance (Top 10 Features)",
  col = "steelblue"
)
```

**Boosting Test AUC:** `r round(auc_boost, 3)`  
**Boosting Sensitivity:** `r round(cm_boost$byClass["Sensitivity"], 3)`  
**Boosting Accuracy:** `r round(cm_boost$overall["Accuracy"], 3)`

## Results: Comparative Evaluation
- We evaluated five models using Accuracy, Sensitivity (Recall), and AUC on the Test Set.
- **Boosting** achieved the highest overall accuracy and the highest sensitivity, meaning it identified the most true positives.
- Logistic, Ridge, and LASSO models performed very similarly in accuracy and AUC, but with lower sensitivity.
- KNN performed the worst, with the lowest AUC, indicating weak separation between classes.

## Model Performance Comparison
```{r final-table, echo=FALSE, message=FALSE, warning=FALSE}
# Create aliases for consistency
cm_knn <- knn_cm
roc_knn <- knn_roc

final_results <- data.frame(
  Model = c("Logistic", "Ridge", "LASSO", "KNN", "Boosting"),
  Accuracy = c(
    cm_baseline$overall["Accuracy"],
    cm_ridge$overall["Accuracy"],
    cm_lasso$overall["Accuracy"],
    cm_knn$overall["Accuracy"],
    cm_boost$overall["Accuracy"]
  ),
  Sensitivity = c(
    cm_baseline$byClass["Sensitivity"],
    cm_ridge$byClass["Sensitivity"],
    cm_lasso$byClass["Sensitivity"],
    cm_knn$byClass["Sensitivity"],
    cm_boost$byClass["Sensitivity"]
  ),
  AUC = c(
    auc(roc_baseline),
    auc(roc_ridge),
    auc(roc_lasso),
    auc_knn,
    auc_boost
  )
)

knitr::kable(final_results, digits = 3)
```

## ROC Curve Comparison
```{r final-roc, echo=FALSE, message=FALSE, warning=FALSE}
roc_all <- rbind(
  data.frame(fpr = 1 - roc_baseline$specificities, tpr = roc_baseline$sensitivities, Model = "Logistic"),
  data.frame(fpr = 1 - roc_ridge$specificities,    tpr = roc_ridge$sensitivities,    Model = "Ridge"),
  data.frame(fpr = 1 - roc_lasso$specificities,    tpr = roc_lasso$sensitivities,    Model = "LASSO"),
  data.frame(fpr = 1 - roc_knn$specificities,      tpr = roc_knn$sensitivities,      Model = "KNN"),
  data.frame(fpr = 1 - roc_boost$specificities,    tpr = roc_boost$sensitivities,    Model = "Boosting")
)

ggplot(roc_all, aes(x = fpr, y = tpr, color = Model)) +
  geom_line(linewidth = 1) +
  geom_abline(linetype = "dashed", color = "grey") +
  labs(
    title = "ROC Curve Comparison for All Models",
    x = "False Positive Rate",
    y = "True Positive Rate"
  ) +
  theme_minimal() +
  theme(legend.position = "right")
```

## Business Impact
* The central trade-off: Boosting is the best predictor, but the **Regularized Logistic Regression** offers the most *interpretable* and *actionable* insights for the bank.
* Sample coefficients: $\beta_{Balance^2}$ = -23.02, $\beta_{Housing}$ = -0.65, $\beta_{JobStudent}$ = 4.064
* The chosen model can lead to cost savings and higher ROI for future campaigns.
* **Image/Plot Idea:** A visual metaphor (e.g., a scale or seesaw) contrasting "High Performance" vs. "High Interpretability."

## Discussion
* Consideration: regulatory/ethical implications in banking and the need to justify predictions (further supporting the value of interpretability).
* Advanced train/test splitting methods like **time-series analysis** were not used.
* Suggest future improvements: Exploring advanced techniques like **resampling methods** (SMOTE) to handle imbalance better or trying.

## References
* UC Irvine Machine Learning Repository. Bank Marketing. https://archive.ics.uci.edu/dataset/222/bank+marketing 
* Github link: https://github.com/dsci445-csu/project-6

```{r image, echo=FALSE, fig.align='center'}
knitr::include_graphics("UCI.png")
```
